rotation_runs2019

### 2019-11-19 inst/documents/rotation_runs2019.Rmd
added change_interval so all changes can only hppen e.g. annually, plus changes now assessed against mean of M&F

# now specify an experiment from the multi-experiment file
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0( "run_rot(rot_interval=",linputs$rot_interval,", ", 
                "n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "male_expo_prop=",signif(linputs$male_expo_prop,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )

>>>>

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0( "run_rot(rot_interval=",linputs$rot_interval,", ", 
                "n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "male_expo_prop=",signif(linputs$male_expo_prop,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "change_interval=",linputs$change_interval,
                #"min_rwr_interval=",linputs$min_rwr_interval,  
                ")\n\n") )

### 2019-11-19 inst/documents/rotations_notes.Rmd
added change_interval so all changes can only hppen e.g. annually, plus changes now assessed against mean of M&F

run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0021, cost=c(0), eff=c(0.98), dom_sel=c(0.51),dom_cos=c(0.63), rr=c(0.8), expo_hi=0.47, male_expo_prop=0.01, coverage=1, migration=0,min_rwr_interval=10, diagnostics = TRUE)

@@

@@

1. find & fix problem with C runs see above
2. implement annual restrictions for sequences

# I think we allow sequence to exit at anytime ? This gives a kind of advantage to sequences, rotations tend to end up with more generations above threshold.

>>>>

run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0021, cost=c(0), eff=c(0.98), dom_sel=c(0.51),dom_cos=c(0.63), rr=c(0.8), expo_hi=0.47, male_expo_prop=0.01, coverage=1, migration=0,min_rwr_interval=10, diagnostics = FALSE)

@@

Ian suggested this could be because we assess frequency after selection and before random mating. So what could be happening is the sequence is stopped because f is above threshold, then random mating happens to take it below threshold.

In which case we could just make sure that insecticide_check is called after mating.
But was tricky to do, partly a result of us assessing just Females for insecticide switch. Now the switch is checked based on mean of M&F.

New setting to make it easier to bug-check

run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.1, max_gen = 50, cost=c(0), eff=c(0.98), dom_sel=c(0.51),dom_cos=c(0.63), rr=c(0.8), expo_hi=0.47, male_expo_prop=0.01, coverage=1, migration=0,min_rwr_interval=10, diagnostics = FALSE)

*storedgen16 freqs i1:0.5172  i2:0.1
gen17 freqs i1:0.4852  i2:0.1292
gen17 i1 freq=0.485228904909616

# 19/11/2019

confirm that insecticide check based on mean of M&F does what I'd expect

trying 100 runs of A1

NO sequence still not doing what I' expect, i.e. for A1 it's going back to insecticide 1 :
Ah probably just because I haven't built and saved ...

run_rot(rot_interval=0, n_insecticides=2, start_freqs=0.077, cost=c(0), eff=c(0.98), dom_sel=c(0.83),
dom_cos=c(0.47), rr=c(0.2), expo_hi=0.69, male_expo_prop=0.17, coverage=1, migration=0,
min_rwr_interval=10)

Currently I have min_gens_switch_back and min_rwr_interval set to 10.
Probably I should set them to 0.

Instead have an input specifiying interval on which insecticides can be changed - applying both to sequence and rotation.

change_interval = 10

if (gens_this_insecticide %% change_interval == 0)

@@

1. find & fix problem with C runs see above
2. add change_interval as an input
3. should I set min_gens_switch_back and min_rwr_interval to 0, they should have no effect

# I think we allow sequence to exit at anytime ? This gives a kind of advantage to sequences, rotations tend to end up with more generations above threshold.
# so now we want to only allow sequences to exit at annual time points (if an option is enabled)
